# Purpose of this file
The purpose of this file is to keep notes and keep track of any decisions that
is made regarding the project. Additionally, a to-do list will be kept here.

## To-do
- Create a github repository for the project                                [X]
- Create an OSF repository for the project                                  [X]
- Link the github repository to the OSF repository                          [X]
- Pre-register the study                                                    [/]


## Decisions


## Other
### 2023-11-27
- Got the prereg template following the instructions from:
```{r}
library(prereg)
```
- Started with the pre-registration template for the study.
- Started investigating the literature for possible models appropriate for analys
is.

### 2023-11-29
- Can use codebook package
```{r}
install.packages("codebook")
```
  - However, I think using sjPlot::view_df() function will work just as well.

- Don't forget to use set.seed() when generating data in either simulations or 
multiple imputations

- Publish figures before publishing (figshare.com) because otherwise the journals
will own your figures!
